Pillar 1 - Sequential Pattern Mining

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
simplify code for confidence/lift

AR$taken <- transactions$taken %>%
  make_AR(
    data_support = d_support$TNT, 
    type_rule = rate.take
    )

@@

  # Confidence and Lift by hand
  separate(
    rhs,
    sep = "_",
    into = c("rhs_course", "rhs_outcome"),
    remove = FALSE
    ) %>%
  group_by(
    lhs, rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = sum(support),
    confidence          = support / lhs.rhsTake.support,
    lift                = confidence / rhs.support
    ) %>%
  ungroup %>%

  # lhs and rhs must be fail, count >= 5
  filter(
    str_detect(lhs, "fail"),
    str_detect(rhs, "fail")
    )
```

@@

  # Confidence and Lift by hand
  separate(
    rhs,
    sep = "_",
    into = c("rhs_course", "rhs_outcome"),
    remove = FALSE
    ) %>%
  group_by(
    lhs, rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = sum(support),
    confidence          = support / lhs.rhsTake.support,
    lift                = confidence / rhs.support
    ) %>%
  ungroup %>%

@@

  # Confidence and Lift
  separate(
    rhs,
    sep = "_",
    into = c("rhs_course", "rhs_outcome"),
    remove = FALSE
    ) %>%
  mutate(
    rhs.taken = str_detect(rhs, "fail|pass")
    ) %>%
  group_by(
    lhs, rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = sum(support * rhs.taken),
    confidence          = support / lhs.rhsTake.support,
    lift                = confidence / rhs.support
    ) %>%
  ungroup %>%

>>>>

AR$taken <- transactions$taken %>%
  make_AR(
    data_support = d_support$TNT, 
    type_rule = rate.take
    )
```

@@

  # Confidence and Lift by hand
  separate(
    rhs,
    sep = "_",
    into = c("rhs_course", "rhs_outcome"),
    remove = FALSE
    ) %>%

  group_by(
    lhs,
    rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = sum(support) # Proba of lhs and taking rhs course
    ) %>%
  ungroup %>%

  mutate(
    confidence = support / lhs.rhsTake.support,
    lift       = confidence / rhs.support
    ) %>%

  # lhs and rhs must be fail
  filter(
    str_detect(lhs, "fail"),
    str_detect(rhs, "fail")
    )
```

@@

  # Confidence and Lift by hand
  separate(
    rhs,
    sep = "_",
    into = c("rhs_course", "rhs_outcome"),
    remove = FALSE
    ) %>%

  group_by(
    lhs, 
    rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = sum(support) # Proba of lhs and taking rhs course
    ) %>%
  ungroup %>%

  mutate(
    confidence = support / lhs.rhsTake.support,
    lift       = confidence / rhs.support
    ) %>%

@@

  # Confidence and Lift
  separate(
    rhs,
    sep = "_",
    into = c("rhs_course", "rhs_outcome"),
    remove = FALSE
    ) %>%
  mutate(
    rhs.taken = str_detect(rhs, "fail|pass")
    ) %>%
  group_by(
    lhs,
    rhs_course
    ) %>%
    mutate(
    lhs.rhsTake.support = sum(support * rhs.taken) # Proba of lhs and taking rhs course
    ) %>%
  ungroup %>%

  mutate(
    confidence = support / lhs.rhsTake.support,
    lift       = confidence / rhs.support
    ) %>%
